### 2019-01-26 thesis_report/results.tex
Updated thesis
Added comparison of spectral calculations

\chapter{Results \& Discussion}

	\comment{We see that the introduction of a zigzag leads to a reduction of the gap}
	\section{Gap/bandstructure as a function of zigzagginess}
		\comment{We discretize the model described in section II and simulate it with Kwant.}
		We implement a tightbinding version of the model described in the Methods section (a two dimensional SNS junction with a Rashba BdG Hamiltonian) using Kwant.

		\begin{figure}[!htb]
		\includegraphics[width=0.95\columnwidth]{figures/bandstructures}
		\caption{Figure of the bandstuctures.
		Where the lines are (blue) $\phi=0$, $B=0$ and (red) $\phi=\pi$, $B \ne 0$.
		and the subplots (a) $z_y=0$, (b) $z_y=\frac{W}{4}$, and (c) $z_y=\frac{W}{2}$, where $W$ is the junction width.
		We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.
		\label{fig:bandstuctures}}
		\end{figure}

@@

	\comment{Introduction of a zigzag leads to localization of the Majorana's}
	\section{Majorana decay length}
		\comment{In a zigzag geometry Majoranas are localized within one segment of zigzag.}

@@

		\begin{figure}[!htb]
		\includegraphics[width=0.95\columnwidth]{figures/wavefunctions}
		\caption{Wavefunctions for different sizes and geometries.
		With (a) a straight system, (b) a zigzag system, (c) a system where the normal region is defined by lines parallel to a sinosoid, and (d) a system with vertically offset sinosoids.
		Inside the figure we indicate the Majorana length (or coherence length) $\xi$ and the topological energy gap $E_\textrm{gap}.$
		We observe that $\xi$ for (a) is orders of magnitude longer and $E_\textrm{gap}$ orders of magnitude smaller than for (b, c, d), meaning that the details of the geometry do not matter.
		\label{fig:wavefunctions}}
		\end{figure}

	\comment{Zigzag Majorana's have a cleaner phase diagram due to the reduction in symmetry class}
	\section{Phase diagram}
		\comment{We calculate the topological phase diagram using the gap size.}
		We calculate the gap by finding the absolute minimum of the spectrum $E_\textrm{gap}=\min{|E(k)|}$.
		Noting the gap closings and the fact we know the topology for the non-zigzag system, we can infer the topology of the system with zigzag modulation. % Bas: I don't understand what is written here

@@

		\begin{figure}[!htb]
		\includegraphics[width=0.95\columnwidth]{figures/phasediagrams}
		\caption{Phase diagrams of a straight system (a, b) and zigzag system (c, d), where (a, c) are $E(\mu, B)$ and (b, d) are $E(\phi, B)$.
		We use a generalized eigenvalue problem to find all phase boundaries at once and find the minimal energy gap by finding the minimum in the spectrum: $\min{E(k)}$.
		\label{fig:phasediagrams}}
		\end{figure}

	\comment{We use our analytical bandstructure to }
	\section{Analytical estimate}

>>>>

% -*- root: ./report.tex -*-
\chapter{Results \& Discussion}
	\comment{Introduction of a zigzag opens up the gap, creates a more stable topological phase diagram, and decreases coherence length of Majorana's}
	\section{Increased isolation and stability of the Majorana state}

	\comment{We see that the introduction of a zigzag leads to a reduction of the gap}
		\subsection{Gap/bandstructure as a function of zigzagginess}
			\comment{We discretize the model described in section II and simulate it with Kwant.}
			We implement a tightbinding version of the model described in the Methods section (a two dimensional SNS junction with a Rashba BdG Hamiltonian) using Kwant.

			\begin{figure}[!htb]
			\centering
			\includegraphics[width=0.55\columnwidth]{figures/bandstructures}
			\caption{Figure of the bandstuctures.
			Where the lines are (blue) $\phi=0$, $B=0$ and (red) $\phi=\pi$, $B \ne 0$.
			and the subplots (a) $z_y=0$, (b) $z_y=\frac{W}{4}$, and (c) $z_y=\frac{W}{2}$, where $W$ is the junction width.
			We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.
			\label{fig:bandstuctures}}
			\end{figure}

@@

		\comment{Introduction of a zigzag leads to localization of the Majorana's}
		\subsection{Majorana decay length}
			\comment{In a zigzag geometry Majoranas are localized within one segment of zigzag.}

@@

			\begin{figure}[!htb]
			\centering
			\includegraphics[width=0.55\columnwidth]{figures/wavefunctions}
			\caption{Wavefunctions for different sizes and geometries.
			With (a) a straight system, (b) a zigzag system, (c) a system where the normal region is defined by lines parallel to a sinosoid, and (d) a system with vertically offset sinosoids.
			Inside the figure we indicate the Majorana length (or coherence length) $\xi$ and the topological energy gap $E_\textrm{gap}.$
			We observe that $\xi$ for (a) is orders of magnitude longer and $E_\textrm{gap}$ orders of magnitude smaller than for (b, c, d), meaning that the details of the geometry do not matter.
			\label{fig:wavefunctions}}
			\end{figure}

		\comment{Zigzag Majorana's have a cleaner phase diagram due to the reduction in symmetry class}
		\subsection{Phase diagram}
			\comment{We calculate the topological phase diagram using the gap size.}
			We calculate the gap by finding the absolute minimum of the spectrum $E_\textrm{gap}=\min{|E(k)|}$.
			Noting the gap closings and the fact we know the topology for the non-zigzag system, we can infer the topology of the system with zigzag modulation. % Bas: I don't understand what is written here

@@

			\begin{figure}[!htb]
			\centering
			\includegraphics[width=0.75\columnwidth]{figures/phasediagrams}
			\caption{Phase diagrams of a straight system (a, b) and zigzag system (c, d), where (a, c) are $E(\mu, B)$ and (b, d) are $E(\phi, B)$.
			We use a generalized eigenvalue problem to find all phase boundaries at once and find the minimal energy gap by finding the minimum in the spectrum: $\min{E(k)}$.
			\label{fig:phasediagrams}}
			\end{figure}

	\section{Finding the mechanism responsible for the increased gap}
		\comment{We use our analytical bandstructure to }
		\subsection{Verification of analytical estimate}
			\begin{figure}[!htb]
			\centering
			\includegraphics[width=0.95\columnwidth]{figures/spectrum_calculation_comparison}
			\caption{Andreev Bound State spectrum of a SNS junction with a tilted in-plane magnetic field, computed using four different methods.}.
			\label{fig:spectrum_calculation_comparison}
			\end{figure}

		\subsection{Estimation of the gap through momentum cutoff}
